Ladies' figure skating in the 2002 Winter Olympics

### 2025-12-14 inst/skating.Rmd
all competitors have strictly positive strength

>>>>

(we note in passing that the Plackett-Luce strengths of every
competitors is strictly positive.  We can see this by observing that:

\begin{alignat*}{4}
\textbf{luka}
&\succ_3\mbox{kopak}      &&\succ_1\mbox{babiakova} &&\succ_3\mbox{giunchi}   &&\succ_1\mbox{hegel}      \\
&\succ_3\mbox{soldatova}  &&\succ_6\mbox{gusmeroli} && \succ_2\mbox{meier}    &&\succ_3\mbox{hubert}     \\
&\succ_4\mbox{onda}       &&\succ_1\mbox{kiashenko} &&\succ_3\mbox{fontana}   &&\succ_2\mbox{maniachenko}\\
&\succ_3\mbox{volchkova}  &&\succ_2\mbox{kettunen}  &&\succ_2\mbox{sebestyen} &&\succ_4\mbox{robinson}   \\
&\succ_3\mbox{butyrskaya} &&\succ_2\mbox{suguri}    &&\succ_1\mbox{cohen}     &&\succ_2\mbox{kwan}       \\
&\succ_1\mbox{slutskaya}  &&\succ_2\mbox{hughes}  \\
&\succ_1\textbf{luka}
\end{alignat*}

and if any competitor has zero BT strength, at least one of the above
successors is false with probability one).
